Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-01-05 writing/CONUS_AOD.Rmd
Removed an unused `library` call.

```{r basics, echo=FALSE}
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(ggpointdensity)
    library(ggdist)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
```

>>>>

```{r basics, echo=FALSE}
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(ggpointdensity)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
```
